\documentclass[a4paper,11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[margin=3cm]{geometry}
\usepackage{lmodern}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{longtable}
\usepackage{xcolor}
\usepackage{colortbl}
\usepackage{fancyhdr}
\usepackage{parskip}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}

% ── Brand colours ──────────────────────────────────────────────────────────────
\definecolor{brand}{HTML}{1E3A5F}
\definecolor{accent}{HTML}{4472C4}
\definecolor{lightgray}{HTML}{F5F5F5}

% ── Section formatting ─────────────────────────────────────────────────────────
\titleformat{\section}{\color{brand}\large\bfseries}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\color{accent}\normalsize\bfseries}{}{0em}{}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0.4pt}
\fancyhead[L]{\textcolor{brand}{\textbf{Visma Enterprise Solutions AS}}}
\fancyhead[R]{\textcolor{brand}{\small Contract ESA-VISMA-2026-007}}
\fancyfoot[C]{\textcolor{gray}{\small Page \thepage\ of \pageref{lastpage}}}

\hypersetup{colorlinks=true, linkcolor=brand, urlcolor=accent}

\begin{document}

% ── Title page block ───────────────────────────────────────────────────────────
\begin{center}
  {\color{brand}\rule{\textwidth}{2pt}}\\[12pt]
  {\color{brand}\huge\bfseries ENTERPRISE SOFTWARE LICENSE AGREEMENT}\\[8pt]
  {\large\bfseries Contract Reference: ESA-VISMA-2026-007}\\[6pt]
  {\large Visma Enterprise Solutions AS \quad $\times$ \quad Allergo Nordic AS}\\[12pt]
  {\color{brand}\rule{\textwidth}{2pt}}
\end{center}

\vspace{12pt}

\noindent
\begin{tabularx}{\textwidth}{lX lX}
  \textbf{Effective Date:} & 1 January 2026 &
  \textbf{Expiry Date:} & 31 December 2028 \\[4pt]
  \textbf{Term:} & 3 years &
  \textbf{Renewal:} & Auto-renew unless 90 days' notice \\[4pt]
  \textbf{Contract Value:} & NOK 2\,160\,000 total &
  \textbf{Annual Value:} & NOK 720\,000 \\[4pt]
  \textbf{Governing Law:} & Kingdom of Norway &
  \textbf{Jurisdiction:} & Oslo District Court \\
\end{tabularx}

\vspace{16pt}

% ── Parties ────────────────────────────────────────────────────────────────────
\section{Parties}

\subsection{Licensor}
\textbf{Visma Enterprise Solutions AS}\\
Org.nr: 956 144 765\\
Karenslyst allé 56, 0277 Oslo, Norway\\
Email: \texttt{contracts@visma.com} \quad Tel: +47 02046\\
Represented by: \textit{Lars Petter Eriksen}, Chief Revenue Officer

\subsection{Licensee}
\textbf{Allergo Nordic AS}\\
Org.nr: 919 345 872\\
Drammensveien 114, 0277 Oslo, Norway\\
Email: \texttt{procurement@allergo-nordic.no} \quad Tel: +47 22 44 88 00\\
Represented by: \textit{Knut Sørensen}, Chief Financial Officer

\section{Scope of Licence}

\subsection{Licensed Software}
The Licensor grants the Licensee a non-exclusive, non-transferable licence to use the following
Visma software modules for the Licensee's internal business operations:

\vspace{8pt}
\begin{tabular}{lll}
  \rowcolor{brand}
  \color{white}\textbf{Module} & \color{white}\textbf{Seats / Scope} & \color{white}\textbf{Annual Licence Fee (NOK)} \\
  \rowcolor{lightgray}
  Visma Business ERP (Finance \& Accounting) & Up to 50 named users & 240\,000.00 \\
  Visma Payroll (Lønn) & All employees (current 87) & 144\,000.00 \\
  \rowcolor{lightgray}
  Visma.net Expense & All employees & 96\,000.00 \\
  Visma AutoInvoice (e-invoicing, EHF) & Unlimited volume & 120\,000.00 \\
  \rowcolor{lightgray}
  Visma Document Centre & 10 TB storage & 72\,000.00 \\
  Visma Analytics (Power BI connector) & 5 named analysts & 48\,000.00 \\
  \midrule
  \textbf{Total Annual Licence Fee} & & \textbf{720\,000.00} \\
  \bottomrule
\end{tabular}

\subsection{Permitted Use}
The Software may only be used by Allergo Nordic AS employees and authorised contractors
within the scope of the Licensee's internal business activities. Sub-licensing, resale,
or use as a service bureau for third parties is strictly prohibited.

\section{Fees and Payment}

\begin{enumerate}[leftmargin=*, label=\arabic{*}.]
  \item The annual licence fee of NOK 720\,000 (excl.\ VAT) shall be invoiced by the
    Licensor on 1 January of each contract year.
  \item VAT at the applicable Norwegian rate (currently 25\%) is payable in addition to
    all fees stated herein.
  \item Payment terms: Net 30 days from invoice date.
  \item Late payment interest: NIBOR + 3\% per annum, accruing from due date.
  \item The Licensor may adjust fees annually by a maximum of CPI + 2\% with 90 days'
    written notice prior to the renewal date.
\end{enumerate}

\section{Support and Maintenance}

\subsection{Standard Support Included}
\begin{itemize}[leftmargin=*]
  \item Access to Visma Help Centre and knowledge base (24/7)
  \item Telephone and email support: Monday--Friday, 08:00--17:00 CET
  \item P1 Critical response: 4 hours; P2 High: 1 business day; P3 Medium: 3 business days
  \item All software updates, patches, and minor version upgrades included at no additional cost
  \item Major version upgrades (e.g.\ Visma Business 7.x $\to$ 8.x) included subject to
    migration assessment
\end{itemize}

\subsection{Uptime SLA}
The Visma cloud-hosted modules carry a 99.9\% monthly uptime SLA. Service credits of 5\% of the
monthly fee apply per 0.1\% below target, capped at 25\% of the monthly fee. SLA credits are
the Licensee's sole remedy for availability failures.

\section{Data Protection}

\begin{enumerate}[leftmargin=*, label=\arabic{*}.]
  \item The Licensor acts as \textbf{Data Processor}; the Licensee acts as \textbf{Data Controller}
    under the EU General Data Protection Regulation (GDPR).
  \item All personal data processed under this Agreement is stored in Visma's data centres
    in Norway and the EU/EEA.
  \item A separate Data Processing Agreement (DPA reference DPA-VISMA-2026-007, Exhibit A) is
    incorporated by reference and forms an integral part of this Agreement.
  \item The Licensor shall notify the Licensee of any confirmed personal data breach within
    24 hours of detection.
  \item Annual ISO/IEC 27001 and ISAE 3402 Type II reports available upon written request.
\end{enumerate}

\section{Intellectual Property}

All intellectual property rights in the Software remain vested in Visma Enterprise Solutions AS
and its licensors. Nothing in this Agreement transfers ownership of the Software to the Licensee.
Allergo Nordic AS retains ownership of all data entered into or generated by the Software.

\section{Confidentiality}

Both parties shall maintain strict confidentiality of all Confidential Information (as defined
in Exhibit B) for the term of this Agreement and for a period of five (5) years after termination.

\section{Limitation of Liability}

\begin{enumerate}[leftmargin=*, label=\arabic{*}.]
  \item Neither party shall be liable for indirect, incidental, or consequential losses.
  \item The Licensor's aggregate liability under this Agreement shall not exceed the total
    fees paid by the Licensee in the twelve (12) months immediately preceding the claim.
  \item Nothing in this Agreement limits liability for death or personal injury caused by
    negligence, fraud, or fraudulent misrepresentation.
\end{enumerate}

\section{Termination}

\begin{enumerate}[leftmargin=*, label=\arabic{*}.]
  \item Either party may terminate for convenience with 90 days' written notice, effective
    at the next contract anniversary date.
  \item Either party may terminate immediately upon material breach not remedied within
    30 days of written notice.
  \item Upon termination, the Licensor shall provide a full data export in machine-readable
    format within 30 days. Data shall be securely deleted within 60 days of export delivery.
\end{enumerate}

\section{Governing Law and Dispute Resolution}

This Agreement is governed by the laws of the Kingdom of Norway. Any dispute shall first be
subject to good-faith negotiations for 30 days. Unresolved disputes shall be referred to
Oslo District Court (\textit{Oslo tingrett}) as the agreed exclusive jurisdiction.

\section{Signatures}

\vspace{12pt}
\begin{tabularx}{\textwidth}{XX}
  \rowcolor{brand}\color{white}\textbf{FOR LICENSOR} &
  \rowcolor{brand}\color{white}\textbf{FOR LICENSEE} \\[12pt]
  Visma Enterprise Solutions AS & Allergo Nordic AS \\[8pt]
  Name: Lars Petter Eriksen & Name: Knut Sørensen \\
  Title: Chief Revenue Officer & Title: Chief Financial Officer \\[16pt]
  Signature: \underline{\hspace{6cm}} & Signature: \underline{\hspace{6cm}} \\[8pt]
  Date: \underline{\hspace{4cm}} & Date: \underline{\hspace{4cm}} \\
\end{tabularx}

\label{lastpage}
\end{document}
